### 2012-08-22 doc/prelim/document/chapters/chimera_codebase/chimera_codebase.tex
Finished initial prelim outline

>>>>

The Chimera code base will be the primary research tool for answering
the questions posed in the previous chapters of the document. We may
not need a chapter for this, but it will likely be a good idea
somewhere in this document to outline the design of the software and
the instrumentation that it will provide.

### 2012-08-22 doc/prelim/document/chapters/fanm/fanm.tex
adding intro and research proposal chapter
Finished initial prelim outline

>>>>

In this chapter we will devise the FANM method. Based on the
background in the previous section, we first need to motivate the
development of this work by pointing out some of the issues with
conventional methods. This includes JFNK coarseness and prohibitively
large Krylov subspace. We can than point out some of the attractive
qualities of the FANM method. Much of this will rely on advanced
concepts including automatic differentiation and on-the-fly residual
and Jacobian generation from nonlinear function evaluations. In
addition, we will want to show that the Newton method will converge
using MCSA as the linear solver. I suspect I will have some
preliminary results for a serial implementation here as I already have
a serial MCSA implemented. Finally, we will want to design the model
problems that we will test FANM with. These should be problems that
have already been worked up in the literature with benchmark-type
solutions.

\section{Issues with Current Nonlinear Methods}
\label{sec:nonlinear_issues}

\section{Automatic Differentiation}
\label{sec:automatic_differentiation}

\section{Residual and Jacobian Generation}
\label{sec:fanm_generation}

\section{Algorithm Outline}
\label{sec:fanm_algorithm_outline}

\section{Model Problems}
\label{sec:fanm_model_problems}

### 2012-08-22 doc/prelim/document/chapters/linear_problem/linear_problem.tex
added outline to the linear and nonlinear problem chapters
adding intro and research proposal chapter
Finished initial prelim outline

\chapter{The Linear Problem}\label{ch:linear_problem}

>>>>

\chapter{The Linear Problem}
\label{ch:linear_problem}

The purpose of this chapter is to provide a full background on solving
linear systems as it relates to this work. It may seem like there is a
lot here, but we really do need it to fully define our new methods and
compare both qualitatively and quantitatively to convential
methods. For example, we need a solid explanation of stationary
methods because MCSA is in fact an acceleration of a stationary method
and therefore shares many properties with them. Subspace methods are
the current class of methods most widely used for sparse systems and
are at the core of the Newton-Krylov methods that we will be comparing
the FANM method with. The most rigorous piece of this chapter should
of course be the stochastic solver definitions, also providing me a
place to include some of my work in this area. Finally,
preconditioning is important for this work, MCSA requires it and
Newton-Krylov methods almost always need some type of
preconditioning. Therefore, we must also discuss these aspects.

\section{Formulation of the Linear System}
\label{sec:linear_system}

\section{Iterative Methods for Solving Sparse Linear Systems}
\label{sec:linear_methods}

\subsection{Stationary Methods}
\label{subsec:stationary_methods}

\subsection{Subspace Methods}
\label{subsec:subspace_methods}

\subsubsection{Conjugate Gradient}
\label{subsubsec:conjugate_gradient}

\subsubsection{GMRES}
\label{subsubsec:gmres}

\subsection{Stochastic Methods}
\label{subsec:stochastic_methods}

\subsubsection{Direct Method}
\label{subsubsec:direct_mc}

\subsubsection{Adjoint Method}
\label{subsubsec:adjoint_mc}

\subsubsection{Sequential Monte Carlo}
\label{subsusbsec:sequential_mc}

\subsection{Monte Carlo Synthetic-Acceleration}
\label{subsec:mcsa}

\section{Preconditioning the Linear System}
\label{sec:linear_preconditioning}

### 2012-08-22 doc/prelim/document/chapters/nonlinear_problem/nonlinear_problem.tex
added outline to the linear and nonlinear problem chapters
updating references
adding intro and research proposal chapter
Finished initial prelim outline

\chapter{The Nonlinear Problem}\label{ch:nonlinear_problem}

>>>>

\chapter{The Nonlinear Problem}
\label{ch:nonlinear_problem}

This work will result in a new and novel nonlinear solver, FANM. To
movitate the development of FANM and thoroughly understand both its
mathematical properties and its qualities as related to other
nonlinear methods, we need a full workup of current iterative methods
for solving nonlinear systems. We should acknowledge operator split
and linearization methods for dealing with nonlinear systems
(e.g. think pressure correction strategies for Navier-Stokes) but the
focus here should be on fully-implicit nonlinear solves that are
amenable to solving tightly-coupled multi-physics systems in a way that
is fully consistent.

The key here will be a full understanding of Newton methods (and they
actually are quite simple compared to some of the linear solver
methods like subspace methods). It is important to understand how the
correction is computed from the Jacobian and how we may improve this
with globalization methods. Although I may not use globalization
methods in my work, they are important enough in practice that we must
be sure that a FANM method is not prohibited from using these. Current
methods, primarily Newton-Krylov methods, will of primary concern here
as these will serve as the baseline for assessing the qualities of a
FANM solver.

Finally, as we will choose transient problems for our models, time
integration in the context of nonlinear systems will be consider and
we will survey applications to model problems in the field ( there is
a vast amount of literature on fully-implicit nonlinear solves for the
Navier-Stokes equations) that will give good benchmarks to test (such
as natural convection and driven cavity problems).

\section{Formulation of the Nonlinear System}
\label{sec:nonlinear_system}

\section{Iterative Methods for Solving Nonlinear Systems}
\label{sec:nonlinear_methods}

\subsection{General Newton Methods}
\label{subsec:newton_methods}

\subsection{Newton-Krylov Methods}
\label{subsec:newton_krylov_methods}

\subsection{Globalization Methods}
\label{subsec:globalization_methods}

\section{Preconditioning the Nonlinear System}
\label{sec:nonlinear_preconditioning}

\section{Time Integration}
\label{sec:time_integration}

\section{Applications to Model Problems}
\label{sec:nonlinear_applications}

### 2012-08-22 doc/prelim/document/chapters/parallel_mcsa/parallel_mcsa.tex
adding intro and research proposal chapter
Finished initial prelim outline

>>>>

For the prelim, I suspect that I will not have a parallel MCSA
algorithm up and running as I will be focusing on generating the code
base needed to build the physics operators and tools for linear and
nonlinear systems analysis. Therefore, here we should focus on
motivating a parallel scheme for this work. We should start by first
looking at current parallel methods for solving linear systems using
the conventional techniques from the previous chapter. It must be
clearly pointed out that for the new hardware coming online, these
methods (or at least their current implementations) will be lacking in
scalability and the potential for resiliency, and therefore a parallel
MCSA is attractive, even if it ultimately does not show performance
gains from a wall time perspective.

Once we have done this, MSOD will need to be defined. The literature
is actually quite lacking here even for reactor physics problems as
this is really bleeding edge. Therefore, I should strive here to more
rigorously define this methodology in terms of solving general linear
systems. Furthermore, we should discuss the aspects of being able to
vary the overlap such that we can generate a spectrum between complete
domain decomposition and complete domain replication. Finally, the
beginnings of the algorithm should be sketched out.

\section{Current Parallel Methodologies for Solving Linear Systems}
\label{sec:current_parallel_methods}

\section{Multiple-Set Overlapping-Domain Decomposition}
\label{sec:msod}

\section{Algorithm Outline}
\label{sec:parallel_mcsa_algorithm_outline}
